### 2019-03-21 5_evaluation.tex
More evaluation text.

>>>>

The number of dependencies per task has a strong influence on the
overhead incurred by each system, as shown in
Figure~\ref{fig:radix}. This plot shows METG(50\%) for the nearest
dependence pattern, when varying the number of dependencies per task
from 0 to 9.

% FIXME: make sure these numbers are up to date for final paper

The ratio in METG between 0 and 3 dependencies per task ranges from
$1.3\times$ to $59\times$ (median $3.0\times$). From 1 to 3
dependencies, the ratio varies from $1.2\times$ to $15\times$ (median
$2.1\times$). The difference is most pronounced in systems which
perform runtime work inline. For example, MPI achieves an METG of 390
ns with 0 dependencies, but this rises to 4.6 us with 3 dependencies,
a factor of $12\times$ increase. This is unsurprising as in the case
of 0 dependencies, no \lstinline[language=C++]{MPI_Isend} calls are
issued at all, so MPI has nothing to do aside from executing kernels
as quickly as possible.

For this reason, we feel especially strongly that it is important to
measure the performance behaviors of programming systems under
realistic workloads, rather than trivial dependencies.
